Tropical Andes montane and lowland forest bird and mammal species GBIF

### 2025-08-14 code/L0/L0_TropicalAndes_frugivores_GBIF.Rmd
Added name and few minor changes;
computer did not like running line 78- return to this

---
title: "Tropical Andes montane and lowland forest bird and mammal species GBIF"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script retrives plant occurrence data from GBIF using the species list from Frugivoria."
data input: "TropicalAndes_Frugivoria_frugivore_traits_species.csv"
data output: "TropicalAndes_GBIF_frugivore_occ.csv and TropicalAndes_GBIF_frugivore_occ_species.csv"
date: "2023-07-25"
output: html_document
---

@@

if (!file.exists(file.path(output_path_L0, file_name))) {
    # Match species names to GBIF  
    gbif_taxon_keys <- frugivore_species$x %>% 
      name_backbone_checklist() %>% # match to backbone 
      filter(!matchType == "NONE") %>% # get matched names
      pull(usageKey) 
    # Make GBIF request
    occ_download(
      pred_in("taxonKey", gbif_taxon_keys),
      pred("hasCoordinate", TRUE),
      pred("hasGeospatialIssue", FALSE),
      pred_in("country",c("EC","CO","VE", "PE", "BO")), 
      format = "SIMPLE_CSV"
    )
    # Download GBIF data
  d <- occ_download_get("0009771-231002084531237",
                        path = output_path_L0, overwrite = TRUE) %>%
    occ_download_import()
  } else {
    cat("File already exists:", file_name, "\n")
    d <- occ_download_get("0009771-231002084531237",
                        path = output_path_L0, overwrite = TRUE) %>%
                        curveocc_download_import()
  }
```

# Subset occurrence to Tropical Andes IUCN Montane and Lowland forest
## Read in Forest shape
```{r}
TropicalAndes_IUCNHabitat_Forest <- read_sf(file.path(data_path, "Forest_sf.shp"), layer = "Forest_sf")
```

>>>>

---
title: "Tropical Andes montane and lowland forest bird and mammal species GBIF"
author: "Hazel J. Anderson, Jenna B. Baljunas"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script retrives plant occurrence data from GBIF using the species list from Frugivoria."
data input: "TropicalAndes_Frugivoria_frugivore_traits_species.csv"
data output: "TropicalAndes_GBIF_frugivore_occ.csv and TropicalAndes_GBIF_frugivore_occ_species.csv"
date: "2023-07-25"
output: html_document
---

@@

if (!file.exists(file.path(output_path_L0, file_name))) {
    # Match species names to GBIF  
    gbif_taxon_keys <- frugivore_species$x %>% 
      name_backbone_checklist() %>% # match to backbone 
      filter(!matchType == "NONE") %>% # get matched names
      pull(usageKey) 
    # Make GBIF request
    occ_download(
      pred_in("taxonKey", gbif_taxon_keys),
      pred("hasCoordinate", TRUE),
      pred("hasGeospatialIssue", FALSE),
      pred_in("country",c("EC","CO","VE", "PE", "BO")), 
      format = "SIMPLE_CSV"
    )
    # Download GBIF data
  d <- occ_download_get("0009771-231002084531237",
                        path = output_path_L0, overwrite = TRUE) %>%
    occ_download_import()
  } else {
    cat("File already exists:", file_name, "\n")
    d <- occ_download_get("0009771-231002084531237",
                        path = output_path_L0, overwrite = TRUE) %>%
                        occ_download_import()
  }
```

# Subset occurrence to Tropical Andes IUCN Montane and Lowland forest
## Read in Forest shape
```{r}
TropicalAndes_IUCNHabitat_Forest <- read_sf(file.path(data_path_L0, "Forest_sf.shp"), layer = "Forest_sf")
```
